---
title: "R Notebook"
output: html_notebook
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# load all the libraries required 
library(dplyr)
library(tidyverse)
library(stringr)
library(scales)
library(ggplot2)
library(stringi)
library(psych)
library(Boruta)
library(mlbench) #for data set
library(caret)
library(tidyverse)
library(randomForest)
```

### Read-in Files
```{r}
# loading the data
google_app_data <- read.csv('Google-Playstore.csv', stringsAsFactors=FALSE, encoding="UTF-8")
#google_app_data <- read.csv('~/Documents/Study/Spring 2021/CS5310/New Data for proj/Google-Playstore.csv',stringsAsFactors=TRUE,header=T,nrow=50000, encoding="UTF-8") 

#Getting the overview information of sample data
str(google_app_data)
summary(google_app_data)
sum(is.na(google_app_data$Rating))
sapply(google_app_data, function(x) sum(is.na(x)))

# Count the percentage of missing values across the dataset
sapply(google_app_data, function(x) round(mean(is.na(x))*100, 2))

# drop missing values
google_app_data <- na.omit(google_app_data)

Class <- google_app_data[c(4)]
google_app_data_Rating <- google_app_data[c(1,2,3,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23)]


#Check for the required features
#These columns will not be useful for us
#App ID, minimum and maximum installs, minimum android version, developer ID, website and email, privacy policy link.
#Removing the above mentioned columns from our data
data.frame(colnames(google_app_data)) 
req_google_app_data <- google_app_data[c(3,4,5,6,9,10,11,12,18,19)]


#Convert KB,MB to normal variable
Value_unity <- ifelse(str_detect(req_google_app_data$Size, 'M'), 1e6, ifelse(str_detect(req_google_app_data$Size, 'K'), 1e3, 1))
req_google_app_data$Size <- Value_unity * as.numeric(str_remove(req_google_app_data$Size, 'K|M'))
```



```{r}
set.seed(998)
rforest_model <- train(y = Class,
                       x = google_app_data_Rating,
                       method = "ranger",
                       importance = "impurity")

nrow(varImp(rforest_model)$importance) #34 variables extracted
regressor <- randomForest(Class ~ . , data = google_app_data_Rating, importance=TRUE) # fit the random forest with default parameter

varImp(regressor) # get variable importance, based on mean decrease in accuracy

varImp(regressor, conditional=TRUE) # conditional=True, adjusts for correlations between predictors

varimpAUC(regressor)



boruta_output <- Boruta(Class ~ ., data=na.omit(google_app_data_Rating), doTrace=0)  

# Check the number of missing values across the dataset
#sapply(google_app_data, function(x) sum(is.na(x)))


data.frame(colnames(req_google_app_data)) 

#Getting the overview information of sample data
str(req_google_app_data)
summary(req_google_app_data$Category)

#Check for data inconsistency 
summary(req_google_app_data$Rating)

#There are NA's which have to be omitted
req_google_app_data <- na.omit(req_google_app_data)

#check for Category variable
sort(unique(req_google_app_data$Category))

#We see there are two Category variables which seem same Education and Educational
#We see there are two Category variables which seem same Music and Music & Audio
req_google_app_data$Category <- str_replace_all(req_google_app_data$Category, "Educational", "Education")
req_google_app_data$Category <- str_replace_all(req_google_app_data$Category, "Music & Audio", "Music")

#check for length of Category variable
length(unique(req_google_app_data$Category))
summary(req_google_app_data$Rating.Count)
sort(unique(req_google_app_data$Installs))
sort(unique(req_google_app_data$Free))
sort(unique(req_google_app_data$Price))
sort(unique(req_google_app_data$Currency))
sort(unique(req_google_app_data$Size))
sort(unique(req_google_app_data$Content.Rating))



sum(is.na(req_google_app_data$Rating))
sapply(req_google_app_data, function(x) sum(is.na(x)))
data.frame(colnames(req_google_app_data)) 
# Count the percentage of missing values across the dataset
sapply(req_google_app_data, function(x) round(mean(is.na(x))*100, 2))


library(forcats) #forcats for fct_infreq function

ggplot(mutate(req_google_app_data, Category = fct_infreq(Category))) + 
  geom_bar(aes(x = Category, fill = ..count..)) +
  coord_flip()

ggplot(mutate(req_google_app_data, Free = fct_infreq(Free))) + 
  geom_bar(aes(x = Free, fill = ..count..))

ggplot(mutate(req_google_app_data, Installs = fct_infreq(Installs))) + 
  geom_bar(aes(x = Installs, fill = ..count..))

#library(corrplot)
#library(RColorBrewer)
#cate <-cor(mtcars)
#corrplot(M, type="upper", order="hclust",
 #        col=brewer.pal(n=8, name="RdYlBu"))

#sort(unique(google_app_data$App.Name))


#.isin(['#NAME?'])].sort_values(by='App Name')
summary(req_google_app_data$Rating)
hist(req_google_app_data$Rating)
```

====================================
Step-2: Explore and prepare the data 
====================================


```{r}
#Transform Size unit(K,M) to Numeric values
Value_unity <- ifelse(str_detect(req_google_app_data$Size, 'M'), 1e6, ifelse(str_detect(req_google_app_data$Size, 'K'), 1e3, 1))
req_google_app_data$Size <- Value_unity * as.numeric(str_remove(req_google_app_data$Size, 'K|M'))

```

Exploring relationships among features using the correlation matrix
```{r}
str(req_google_app_data)
# exploring relationships among features: correlation matrix
cor(req_google_app_data[c("Rating.Count", "Price","Size" , "Rating")])
```
Observations: 
  1. Rating and Rating.Count: No correlation
  2. Rating and Price: No correlation
  3. Rating.Count and Price: No correlation
  4. 
SIZE NEED TO BE FIXED


Visualizing relationships among features ñ the scatterplot matrix
```{r}
# visualing relationships among features: scatterplot matrix
# pairs(req_google_app_data[c("Rating.Count", "Price","Size" , "Rating")])
pairs.panels(req_google_app_data[c("Rating.Count", "Price","Size" , "Rating")])
```

=================================
Step-3: Train a model on the data 
=================================

```{r}
rmodel <- lm(Rating ~ Category + Rating.Count + Installs + Free + Price + Size + Content.Rating, data = req_google_app_data)
```


=======================================
Step-4: Evaluate the model performance 
=======================================
```{r}
summary(rmodel)
```
	Observations: 
	1. Residuals section provides summary statistics for the errors in our predictions
		error = actual - predicted 
	2. Significance level: p value should be lower than 0.001, 0.05, or 0.1 to prove that the effect is significant and not just by chance 
	3. Multiple R-squared value: Provides a measure of how well our model as a whole explains the values of the dependent variable.
		Here,Since the R-squared value is 0.5363 --> the model explains nearly 53% of the variation in the dependent variable 
		
		Adjusted R-squared value corrects R-squared by penalizing models with a large number of independent variables.


=======================================
Step-5: Imrpoving the model performance
=======================================
```{r}

```

--------------------------------------------------------------------------------------------

```{r}
google_app_data <- read.csv('Google-Playstore.csv', stringsAsFactors=FALSE, encoding="UTF-8")
```

googleplaystore_user_reviews


